### 2015-01-10 paper/Content/03conclusion.tex
Framework --> SDK

\IEEEPARstart{I}{n} course of this research paper we have analyzed the characteristics given by the \emph{Android} Framework and have identified 
principle components which are generally used for developing an \emph{Android} applications. Those components have been examined regarding their composition and characteristics. 
Applying MVP offers various benefits like a better testability [……], but the paper has shown that it is often hard to define the roles 
of the \emph{Android} components considering MVP and to embed those components into the whole MVP model. But finally we can offer an MVP approach 
for \emph{Android} and a corresponding prototype app demonstrating how principle \emph{Android} components can be structured for applying MVP.

However, just the essential framework components have been examined regarding their MVP compatibility and used in the prototype. 
The MVP pattern for \emph{Android} would only succeed in practice if a wide bandwidth of framework components was adaptable. 
In course of additional research studies addressing this topic we recommend to examine further frameworks components and 
evaluate them regarding their MVP compatibility by implementing prototypes.

>>>>

\IEEEPARstart{I}{n} course of this research paper we have analyzed the characteristics given by the \emph{Android} SDK and have identified 
principle components which are generally used for developing an \emph{Android} applications. Those components have been examined regarding their composition and characteristics. 
Applying MVP offers various benefits like a better testability [……], but the paper has shown that it is often hard to define the roles 
of the \emph{Android} components considering MVP and to embed those components into the whole MVP model. But finally we can offer an MVP approach 
for \emph{Android} and a corresponding prototype app demonstrating how principle \emph{Android} components can be structured for applying MVP.

However, just the essential SDK components have been examined regarding their MVP compatibility and used in the prototype. 
The MVP pattern for \emph{Android} would only succeed in practice if a wide bandwidth of SDK components was adaptable. 
In course of additional research studies addressing this topic we recommend to examine further SDK components and 
evaluate them regarding their MVP compatibility by implementing prototypes.
